
\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
%\usepackage[margin=3cm]{geometry}

\pagestyle{empty}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

\begin{document}

\vspace*{0.5em}

\begin{center}
{\LARGE \textbf{Jeremiah Mahler}}

\vspace{0.2em}

990 Normal Ave\ \ \textbullet
\ \ Chico, CA 95928
\\
(530) 588-0103\ \ \textbullet
\ \ jmmahler@gmail.com
\end{center}

\vspace{0.5em}

\subsection*{Experience}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{McLeod Institute of Simulation Sciences}}
		{\textbf{Chico, CA}}
	\\
	\headerrow
		{\emph{Research Assistant}}
		{\emph{March 2012 -- Present}}
	
	\begin{itemize}
		\item background
		\begin{itemize}
			\item CSU Chico Research project led by Dr. Roy Crosbie,
			Dr. John Zenor, Dr. Kurtis Kredo II and others.
			\item Develops FPGA based electric motor simulations.
			\item Contracts with The Office of Naval Research as part of
				their Unmanned Underwater Vehicle project.
		\end{itemize}

		\item Developed PCIe interfaces for Xilinx FPGAs.
%			\begin{itemize}
%			\item Device drivers in Linux and Windows.
%			\item FPGA code establish FIFO interface.
%			\end{itemize}
		\item Developed Ethernet interfaces for Xilinx FPGAs.
%			\begin{itemize}
%			\item Socket interface
%			\item FPGA code to process packets (ARP, IP).
%			\end{itemize}
		\item Developed Matlab/Simulink interfaces for motor simulations.
		\item Led transition to Git for version control.
			\begin{itemize}
			\item Resulted in a substantial increase in productivity of
					the entire project.
			\end{itemize}
	\end{itemize}
\end{itemize}

\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Open Source Developer}}
		{\textbf{github.com/jmahler}}
	\\
	\headerrow
		{\emph{}}
		{\emph{2007 -- Present}}
	\begin{itemize}
		\item mips-cpu - MIPS CPU implemented in Verilog.
		\item ldd - Linux device driver examples.
		\item sprinklerpi - Sprinkler control with Linux on a RasberryPI.
		\item libtext-loouptable-perl - Text based look up table operations for Perl.
	\end{itemize}

\end{itemize}



\begin{itemize}
	\parskip=0.1em

	\item
	\headerrow
		{\textbf{Chico Volkswagen}}
		{\textbf{Chico, CA}}
	\\
	\headerrow
		{\emph{Master Technician}}
		{\emph{February 2007 -- May 2009}}
	\begin{itemize}
		\item Performed all types of automotive repair and diagnosis.
		\item ASE Master Certified with Advanced L1
		\item BAR California Certified, Basic Area 2008
		\item Volkswagen Certified for 2007, 2008
		\item Reached stage 3/5 of 2008 Volkswagen Service Qualification World Championship
	\end{itemize}

\end{itemize}


\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{California State University Chico}}
		{\textbf{Chico, CA}}
	\\
	\headerrow
		{\emph{B.S. Electrical Engineering}}
		{\emph{2011 -- 2014}}
	\begin{itemize}
		\item Graduating Spring 2014.
		\item Nominated to Phi Kappa Phi (2012).
	\end{itemize}

\end{itemize}

\end{document}
